Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-22 paper/structureScene.tex
cite Mallat 2012

\usepackage{color}
\newcommand{\gl}[1]{\textcolor{red}{Gregoire : #1}}
\newcommand{\mr}[1]{\textcolor{magenta}{Mathias : #1}}
\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu : #1}}

@@

By resorting to wavelet modulus, as opposed to Fourier transform modulus, the resulting features are provably stable to small time warps,
in the sense of Lipschitz regularity with respect to diffeomorphisms \cite{Mallat2010}.
Besides invariance to translation, this stability property is crucial in signal classification, as it entails a guarantee of robustness to small variations in pitch, reverberation, and rhythmic organization of events, which make up an important part of the intra-class variability among natural sounds.

>>>>

\usepackage{color}
\newcommand{\vl}[1]{\textcolor{orange}{Vincent : #1}}
\newcommand{\gl}[1]{\textcolor{red}{Gr\'egoire : #1}}
\newcommand{\ja}[1]{\textcolor{magenta}{Joakim : #1}}
\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu : #1}}

@@

By resorting to wavelet modulus, as opposed to Fourier transform modulus, the resulting features are provably stable to small time warps,
in the sense of Lipschitz regularity with respect to diffeomorphisms \cite{Mallat2012}.
Besides invariance to translation, this stability property is crucial in signal classification, as it entails a guarantee of robustness to small variations in pitch, reverberation, and rhythmic organization of events, which make up an important part of the intra-class variability among natural sounds.
